Which Scenario Should We Design For? Insights from House Elevation on the Multiple PDF Problem

### 2021-12-10 papers/agu21/combining.tex
Some more edits from AGU

\begin{block}{synthesizing pdfs for decision relevance}
    If there are only a few PDFs, then qualitative comparisions (\eg, \cref{fig:tradeoffs}) may be sufficient.
    With \emph{many} PDFs (\eg, \cref{fig:boxplots}), further synthesis is needed.

    We consider the \emph{common case} of assessing decisions using simulations (SOWs) from each of $K$ PDFs.
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{bayes-rdm.pdf}
        \caption{
            Sketch of the ``Prior Model Averaging'' framework.
        }\label{fig:flowchart}
    \end{figure}
\end{block}

>>>>

\begin{block}{synthesizing pdfs for decision relevance}
    If there are only a few PDFs, then qualitative comparisions (\eg, \cref{fig:tradeoffs}) may be sufficient.
    With \emph{many} PDFs (\eg, \cref{fig:boxplots}, refs.~\cite{ruckert_coastal:2019,sharma_rcp:2021}), further synthesis is needed.\\[0.5em]
    We consider the \emph{common case} of assessing decisions using simulations (SOWs) from each of $K$ PDFs.
    A system model $f$ quantifies the outcomes $u$ of taking decision $x$ under SOW $s$.
    Examining all SOWs created by a given model yields \emph{scenario-conditional optimization} (\cref{fig:tradeoffs}).
    To synthesize across PDFs, a weighting approach based on Bayesian Model Averaging \cite{wong_surge:2018,Yao:2018bu} is used.
    \begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{bayes-rdm.pdf}
        \caption{
            Sketch of the ``Prior Model Averaging'' framework.
        }\label{fig:flowchart}
    \end{figure}
\end{block}

### 2021-12-10 papers/agu21/doesnt-fit-all.tex
Some more edits from AGU

\begin{block}{one size doesn't fit all!}
    \begin{itemize}
        \item Tailoring guidance to specific building characteristics can improve outcomes
        \item Elevating to ``\gls{bfe} plus a foot'' is not always optimal \cite{xian_elevation:2017,zarekarizi_suboptimal:2020}
        \item Both over- and under-building can be costly \cite{ansar_bigisfragile:2017,DossGollin:2019}
    \end{itemize}
    \begin{framed}
        \begin{figure}
            \centering
            \includegraphics[width=0.475\textwidth]{5.5.pdf}%
            \includegraphics[width=0.475\textwidth]{7.5.pdf}
            \caption{
                Tradeoffs between construction cost and expected NPV lifetime costs for houses initially situated (L) \SI{2.5}{ft} and (R) \SI{0.5}{ft} below the \gls{bfe} under \gls{rcp} 6.0 with fast BRICK dynamics.
                Note $y$-axes are not equal.
            }
        \end{figure}
    \end{framed}
\end{block}

>>>>

\begin{block}{one size doesn't fit all!}
    \begin{itemize}
        \item Tailoring guidance to specific building characteristics can improve outcomes
        \item Elevating to ``\gls{bfe} plus a foot'' is not always optimal \cite{xian_elevation:2017,zarekarizi_suboptimal:2020}
        \item Both over- and under-building can be costly \cite{ansar_bigisfragile:2017,DossGollin:2019}
    \end{itemize}
    \begin{framed}
        \begin{figure}
            \centering
            \includegraphics[width=0.475\textwidth]{5.5.pdf}%
            \includegraphics[width=0.475\textwidth]{7.5.pdf}
            \caption{
                Tradeoffs between construction cost and expected NPV lifetime costs for houses initially situated (L) \SI{2.5}{ft} and (R) \SI{0.5}{ft} below the \gls{bfe} under \gls{rcp} 6.0 with fast BRICK \cite{wong_brick0.2:2017} dynamics.
                Note $y$-axes are not equal.
            }
        \end{figure}
    \end{framed}
\end{block}

### 2021-12-10 papers/agu21/not-equally-plausible.tex
Some more edits from AGU

\begin{block}{we're always }
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{lsl_priors.pdf}
        \caption{
            If we weight all scenarios equally, then our projection of MSL in 2100 follows the sampling distribution.
            This may or may not accurately reflect available information.
        }
    \end{figure}
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{inference_weights.pdf}
        \caption{
            The prior model averaging approach (\cref{fig:flowchart}) re-weights PDFs based on their distance, and that of other PDFs available, from the (ideally coproduced!) prior.
        }
    \end{figure}
\end{block}

>>>>

\begin{block}{different beliefs emphasizes different possibilities}
    The prior model averaging approach (\cref{fig:flowchart}) assigns a weight to each PDF based on their
    \begin{itemize}
        \item The prior can't be ``right''  \cite{gelman_workflow:2020,gelman_philosophy:2013} or ``scenario neutral'' \cite{quinn_exploratory:2020}
        \item let's at least \textbf{make assumptions transparent}!
    \end{itemize}
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{lsl_priors.pdf}
        \caption{
            If we weight all scenarios equally, then our projection of MSL in 2100 follows the sampling distribution; this may or may not reflect available information.        }
    \end{figure}
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{inference_weights.pdf}
        \caption{
            Weights assigned to each PDF (from \cref{fig:boxplots}) under each prior considered.
            Horizontal line shows the weight given to each under an implicit uniform assumption.
        }
    \end{figure}
\end{block}
